Imposing a Weight Norm Constraint for Neuro-Adaptive Control

### 2025-06-20 presentation/presentation.tex
after rehearser ; prof cmt added

% \documentclass[8pt, aspectratio=169, handout]{beamer} \setbeameroption{show notes on second screen}
% \documentclass[8pt, aspectratio=169, handout]{beamer} \setbeameroption{show only notes}
\documentclass[8pt, aspectratio=169]{beamer}

@@

          \onslide<3->
          {
            \begin{itemize}
              \item Add a \ctxt{airforceblue}{stabilizing term }(\eg $ -\lambda \estwth $) to adaptation law.
              \item Construct a \ctxt{airforceblue}{invariant set }of the NN weights.
            \end{itemize}

            \begin{equation}
              \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \ctxt{awesome}{\lambda \estwth}
            \end{equation}
          }

@@

  \textbf{Contribution 1: Unified Optimization Framework} 
  \onslide<2->
  {
    \begin{itemize}
      \item Trajectory tracking and constraint handling are formulated as a \ctxt{airforceblue}{unified constrained optimization } problem.
      \item The \ctxt{awesome}{conventional controllers } does not required.
      \begin{itemize}
        \item Nominal model knowledge is not required for the conventional controllers.
      \end{itemize}
    \end{itemize}
  }

@@

    \begin{itemize}
      \item \ctxt{awesome}{Find } NN weights $\estwth$,
      \item That \ctxt{airforceblue}{minimize } objective function $J(\cdot)$,
        \begin{equation}\label{eq:obj}
          J(\mv{r};\estwth)
          := 
          \frac{1}{2} \mv{r}^\top \mv{r}.
        \end{equation}
        \begin{itemize}
          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is \ctxt{awesome}{filtered tracking error},
        \end{itemize}
      \item while satisfying the following \ctxt{awesome}{constraints}:
        \begin{itemize}
          \item \ctxt{airforceblue}{Boundedness } of the NN weights $\estwth$.
          \item \ctxt{airforceblue}{Saturation } of the control input $\mv{\tau}$.
        \end{itemize}
    \end{itemize}

@@

    \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
      For the \ctxt{airforceblue}{dynamical system } described in \eqref{eq:sys}, the \ctxt{awesome}{neuro-adaptive controller } in \eqref{eq:input} with the \ctxt{airforceblue}{weight adaptation laws } in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the \ctxt{airforceblue}{boundedness } of the \ctxt{awesome}{filtered error } $\mv{r}$ and the \ctxt{awesome}{weight estimate } $\estwth$, under the control input constraints satisfying Assumption 1 and 2. This holds under the \ctxt{awesome}{weight norm constraint } \eqref{eq:cstr:weight}.
    \end{block}

@@

  \begin{itemize}
    \item Only \ctxt{awesome}{weight norm constraint } is considered in this presentation (for \textbf{ECC}).
    \item Input saturation constraints are not considered.
    \item For simplicity, \ctxt{airforceblue}{single hidden layer NN} is used.
  \end{itemize}

@@

    \begin{itemize}
      \item NAC-CO denotes the proposed controller based on \ctxt{airforceblue}{constrained optimization }.
      \item For NAC-L2 and NAC-eMod, the \ctxt{awesome}{stabilizing terms } $-\lambda\estwth$ and $\rho\norm{\mv{r}}\estwth$ ensures the weights boundedness, respectively.
    \end{itemize}

    \begin{table}
      \renewcommand{\arraystretch}{1.5}
      % \caption{Controller Properties.}
      \centering
      \begin{tabular}{c m{20em} c c c }
      \hline
      \textbf{Name} & \textbf{Description} & \textbf{Adaptation Law} \\
      \hline
      \hline 
        \multirow{2}{*}{NAC-L2} & NAC with $L_2$-regularization \tiny{(equal to $\sigma$-modification)} & \multirow{2}{*}
        {$
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\lambda}\estwth\right)
        $}
        \\
          & ($\ctxt{awesome}{\lambda}$ stabilizes $\estwth$ towards origin) &
        \\
      \hline
        \multirow{2}{*}{NAC-eMod} & NAC with $\epsilon$-modification & \multirow{2}{*}
        {$
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\rho}\norm{\tilde{\mv{r}}}\estwth\right)
        $}
        \\
        & ($\ctxt{awesome}{\rho}$ stabilizes proportionally to filtered error $\mv{r}$) &
        \\
      \hline
        \multirow{2}{*}{NAC-CO} & Constrained Optimization-based NAC & 
        $
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\sum_{j\in\mathcal{I}}\lambda_j\ppfrac{c_j}{\estwth}\right)
        $ 
        \\
          (proposed) & ($\ctxt{awesome}{\beta_j}$ determines $\lambda_j$ adaptation speed) &
        $
          \ddt\lambda_j = \ctxt{awesome}{\beta_j} c_j$, and $\lambda_j \leftarrow \max(\lambda_j,0)
        $
        \\
      \hline
      \end{tabular}
      \label{table:sys:param}
    \end{table}

    \onslide<2->
    {
      \centering
      \begin{minipage}{0.75\textwidth}
        \begin{block}{Simulation Objective}
          By \ctxt{airforceblue}{varying the parameters }, \ie $\beta_j$, $\lambda$, and $\rho$, the parameter dependencies will be investigated.
        \end{block}
      \end{minipage}
    }

@@

\note[enumerate]
{
  \item For comparative study, we used two existing methods: L2-regularization (NAC-L2) and $\epsilon$-modification (NAC-eMod).
  \item Please, note that the L2-regularization is equal to the $\sigma$-modification.
  \item In summary, the NAC-L2 and NAC-eMod use the stabilizing terms $-\lambda\estwth$ and $\rho\norm{\mv{r}}\estwth$, respectively, to ensure the boundedness of the weights.
  \item While the NAC-CO is the proposed method, which uses the Lagrange multipliers $\lambda_j$ to ensure the boundedness of the weights.
  \item The simulation is mainly conducted to investigate dependencies of the crucial parameters, \ie $\beta_j$, $\lambda$, and $\rho$.
}

@@

      \small
      {
        \begin{itemize}
          \item<+-> The parameters ranged from $0.001$ to $1$ across 10 samples.
          \item<+-> NAC-L2 shows the \ctxt{awesome}{worst performance } with high variance.
          \item<+-> NAC-CO (proposed) shows the \ctxt{airforceblue}{best performance } and \ctxt{airforceblue}{lowest variance}.
          \item<+-> This result is because, 
            \begin{itemize}
              \item<+-> NAC-L2 and NAC-eMod are \ctxt{airforceblue}{biased towards the origin}. $\ddtt\estwth=-\alpha(\pptfrac{J}{\estwth}+\ctxt{awesome}{\lambda\estwth})$ (NAC-L2) or $+\ctxt{awesome}{\rho\norm{\mv{r}}\estwth}$ (NAC-eMod), proportionally to $\lambda$ and $\rho$, respectively.
              % \item<+-> $\beta_j$ in NAC-CO (proposed) only determines the \ctxt{airforceblue}{update speed } of the Lagrange multipliers $\lambda_j$, \ie $\ddtt\lambda_j=\beta_j c_j$.
              % \begin{itemize}
                \item<+-> $\ctxt{awesome}{-\lambda_j\pptfrac{c_j}{\estwth}}$ in NAC-CO (proposed) (\ie $\ddtt\estwth=-\alpha(\pptfrac{J}{\estwth}+\ctxt{awesome}{\lambda_j\pptfrac{c_j}{\estwth}})$) \ctxt{airforceblue}{disappears } when constraints are inactive (\ie $c_j<0$, and $\lambda=\beta_jc_j$ and $\lambda_j\leftarrow\max(\lambda_j,0)$). %
              % \end{itemize}
            \end{itemize}
        \end{itemize}
      }

@@

\note[enumerate]
{
  \item The parameters were varied from $0.001$ to $1$ across 10 samples.
  \item The box-and-whisker plots show the distribution of the tracking error ISE (Integral of Squared Error).
  \item The NAC-L2 shows the worst performance with high variance, while the NAC-CO (proposed) shows the best performance with the lowest variance.
  \item The reason is that the NAC-L2 and NAC-eMod are biased towards the origin, especially, proportionally to the parameters $\lambda$ and $\rho$, respectively.
  \item On the other hand, the term that biases the weights towards the origin in NAC-CO, is removed when the constraints are inactive, \ie $c_j<0$.
  \item Therefore, the NAC-CO can track the desired trajectory without being biased, when the constraints are inactive.
}

@@

  \begin{itemize}
    \item<+-> NAC-CO (proposed) showed the \ctxt{airforceblue}{weight norms } are bounded \ctxt{awesome}{under pre-defined constraint } $\overline{\theta}=20$.
    \item<+-> NAC-L2 and NAC-eMod showed the bounded weight norms, but they \ctxt{awesome}{depended } on the parameters $\lambda$ and $\rho$, respectively.
    % \item<+-> As the parameters $\lambda$ and $\rho$ increase, the weight norms of NAC-L2 and NAC-eMod biased towards the origin, which may lead to suboptimal performance.
    \item<+-> In other words, NAC-CO tracked the desired trajectory with a \ctxt{airforceblue}{smaller weight } norm than NAC-L2 and NAC-eMod.
  \end{itemize}

@@

  \begin{itemize}
    \item NAC-CO (proposed) \ctxt{airforceblue}{outperformed } NAC-L2 and NAC-eMod in terms of \ctxt{awesome}{tracking performance}.
    \item As the weights are \ctxt{awesome}{biased }towards the origin proportionally to the parameters $\lambda$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward \ctxt{airforceblue}{suboptimal points}.
  \end{itemize}

@@

\note[enumerate]
{
  \item The tracking performance of the three methods are shown.
  \item The NAC-CO (proposed) outperformed the other two methods in terms of tracking performance.
  \item As the weights are biased towards the origin proportionally to the parameters $\lambda$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward suboptimal points.
}

@@

  \centering
  \includemedia[
      width=0.64\linewidth,
      height=0.36\linewidth,
      activate=onclick,
      addresource=animation.mp4,
      flashvars={
        source=animation.mp4
        &autoPlay=true
        &loop=true
      }
    ]{}{VPlayer.swf}

@@

  \textbf{Summary of Contributions}
  \begin{itemize}
    \item Proposed a novel constrained optimization-based neuro-adaptive control (CONAC) method.
    \item Adaptation laws are derived using \ctxt{airforceblue}{constrained optimization method}.
    \item The proposed method guarantees the \ctxt{awesome}{stability }of the system and the boundedness of the NN weights.
    \item Feasibility of the proposed method is validated through numerical simulations.
  \end{itemize}

>>>>

\documentclass[8pt, aspectratio=169, handout]{beamer} 
% \documentclass[8pt, aspectratio=169, handout, draft]{beamer} 
% \documentclass[8pt, aspectratio=169, handout]{beamer} \setbeameroption{show only notes}
% \documentclass[8pt, aspectratio=169]{beamer}

@@

          \onslide<3->
          {
            \begin{itemize}
              \item Add a \ctxt{airforceblue}{stabilizing term }(\eg $ -\sigma \estwth $) to adaptation law.
              \item Construct a \ctxt{airforceblue}{invariant set }of the NN weights.
            \end{itemize}

            \begin{equation}
              \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \ctxt{awesome}{\sigma \estwth}
            \end{equation}
          }

@@

  \textbf{Contribution 1: Constrained Unified Optimization Framework} 
  \onslide<2->
  {
    \begin{itemize}
      \item Trajectory tracking and constraint handling are formulated as a \ctxt{airforceblue}{unified constrained optimization } problem.
      \item The \ctxt{awesome}{conventional controllers } does not required.
      \begin{itemize}
        \item Nominal model knowledge is not required for the conventional controllers.
      \end{itemize}
    \end{itemize}
  }

@@

    \begin{itemize}
      \item \ctxt{awesome}{Find } NN weights $\estwth$,
      \item That \ctxt{airforceblue}{minimize } objective function $J(\cdot)$,
        \begin{equation}\label{eq:obj}
          J(\mv{r};\estwth)
          := 
          \frac{1}{2} \mv{r}^\top \mv{r}.
        \end{equation}
        \begin{itemize}
          \item where $\mv{r} := \ddt\mv{e} + \sigma\mv{e}$ is \ctxt{awesome}{filtered tracking error},
        \end{itemize}
      \item while satisfying the following \ctxt{awesome}{constraints}:
        \begin{itemize}
          \item \ctxt{airforceblue}{Boundedness } of the NN weights $\estwth$.
          \item \ctxt{airforceblue}{Saturation } of the control input $\mv{\tau}$.
        \end{itemize}
    \end{itemize}

@@

    \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
      For the \ctxt{airforceblue}{dynamical system } described in \eqref{eq:sys}, the \ctxt{awesome}{neuro-adaptive controller } in \eqref{eq:input} with the \ctxt{airforceblue}{weight adaptation laws } in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the \ctxt{airforceblue}{boundedness } of the \ctxt{awesome}{filtered error } $\mv{r}$ and the \ctxt{awesome}{weight estimate } $\estwth$, under the \ctxt{airforceblue}{control input constraints} satisfying Assumption 1 and 2. This holds under the \ctxt{awesome}{weight norm constraint } \eqref{eq:cstr:weight}.
    \end{block}

@@

  \begin{itemize}
    \item Only \ctxt{awesome}{weight norm constraint } is considered in this presentation (for \textbf{†his Conference paper}).
    \item Input saturation constraints are not considered.
    \item For simplicity, \ctxt{airforceblue}{single hidden layer NN} is used.
  \end{itemize}

@@

    \begin{itemize}
      \item NAC-CO denotes the proposed controller based on \ctxt{airforceblue}{constrained optimization }.
      \item For NAC-L2 and NAC-eMod, the \ctxt{awesome}{stabilizing terms } $-\sigma\estwth$ and $\rho\norm{\mv{r}}\estwth$ ensures the weights boundedness, respectively.
    \end{itemize}

    \begin{table}
      \renewcommand{\arraystretch}{1.5}
      % \caption{Controller Properties.}
      \centering
      \begin{tabular}{c m{20em} c c c }
      \hline
      \textbf{Name} & \textbf{Description} & \textbf{Adaptation Law} \\
      \hline
      \hline 
        \multirow{2}{*}{NAC-L2} & NAC with $L_2$-regularization \tiny{(equal to $\sigma$-modification)} & \multirow{2}{*}
        {$
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\sigma}\estwth\right)
        $}
        \\
          & ($\ctxt{awesome}{\sigma}$ stabilizes $\estwth$ towards origin) &
        \\
      \hline
        \multirow{2}{*}{NAC-eMod} & NAC with $\epsilon$-modification & \multirow{2}{*}
        {$
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\rho}\norm{\tilde{\mv{r}}}\estwth\right)
        $}
        \\
        & ($\ctxt{awesome}{\rho}$ stabilizes proportionally to filtered error $\mv{r}$) &
        \\
      \hline
        \multirow{2}{*}{NAC-CO} & Constrained Optimization-based NAC & 
        $
          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\sum_{j\in\mathcal{I}}\lambda_j\ppfrac{c_j}{\estwth}\right)
        $ 
        \\
          (proposed) & ($\ctxt{awesome}{\beta_j}$ determines $\lambda_j$ adaptation speed) &
        $
          \ddt\lambda_j = \ctxt{awesome}{\beta_j} c_j$, and $\lambda_j \leftarrow \max(\lambda_j,0)
        $
        \\
      \hline
      \end{tabular}
      \label{table:sys:param}
    \end{table}

    \onslide<2->
    {
      \centering
      \begin{minipage}{0.75\textwidth}
        \begin{block}{Simulation Objective}
          By \ctxt{airforceblue}{varying the parameters }, \ie $\beta_j$, $\sigma$, and $\rho$, the parameter dependencies will be investigated.
        \end{block}
      \end{minipage}
    }

@@

\note[enumerate]
{
  \item For comparative study, we used two existing methods: L2-regularization (NAC-L2) and $\epsilon$-modification (NAC-eMod).
  \item Please, note that the L2-regularization is equal to the $\sigma$-modification.
  \item In summary, the NAC-L2 and NAC-eMod use the stabilizing terms $-\sigma\estwth$ and $\rho\norm{\mv{r}}\estwth$, respectively, to ensure the boundedness of the weights.
  \item While the NAC-CO is the proposed method, which uses the Lagrange multipliers $\lambda_j$ to ensure the boundedness of the weights.
  \item The simulation is mainly conducted to investigate dependencies of the crucial parameters, \ie $\beta_j$, $\sigma$, and $\rho$.
}

@@

      \small
      {
        \begin{itemize}
          \item<+-> The parameters ranged from $0.001$ to $1$ across 10 samples.
          \item<+-> NAC-L2 shows the \ctxt{awesome}{worst performance } with high variance.
          \item<+-> NAC-CO (proposed) shows the \ctxt{airforceblue}{best performance } and \ctxt{airforceblue}{lowest variance}.
          \item<+-> This result is because, 
            \begin{itemize}
              \item<+-> NAC-L2 and NAC-eMod are \ctxt{airforceblue}{biased towards the origin}. $\ddtt\estwth=-\alpha(\pptfrac{J}{\estwth}+\ctxt{awesome}{\sigma\estwth})$ (NAC-L2) or $+\ctxt{awesome}{\rho\norm{\mv{r}}\estwth}$ (NAC-eMod), proportionally to $\sigma$ and $\rho$, respectively.
              % \item<+-> $\beta_j$ in NAC-CO (proposed) only determines the \ctxt{airforceblue}{update speed } of the Lagrange multipliers $\lambda_j$, \ie $\ddtt\lambda_j=\beta_j c_j$.
              % \begin{itemize}
                \item<+-> $\ctxt{awesome}{-\lambda_j\pptfrac{c_j}{\estwth}}$ in NAC-CO (proposed) (\ie $\ddtt\estwth=-\alpha(\pptfrac{J}{\estwth}+\ctxt{awesome}{\lambda_j\pptfrac{c_j}{\estwth}})$) \ctxt{airforceblue}{disappears } when constraints are inactive (\ie $c_j<0$, and $\lambda=\beta_jc_j$ and $\lambda_j\leftarrow\max(\lambda_j,0)$). %
              % \end{itemize}
            \end{itemize}
        \end{itemize}
      }

@@

\note[enumerate]
{
  \item The parameters were varied from $0.001$ to $1$ across 10 samples.
  \item The box-and-whisker plots show the distribution of the tracking error ISE (Integral of Squared Error).
  \item The NAC-L2 shows the worst performance with high variance, while the NAC-CO (proposed) shows the best performance with the lowest variance.
  \item The reason is that the NAC-L2 and NAC-eMod are biased towards the origin, especially, proportionally to the parameters $\sigma$ and $\rho$, respectively.
  \item On the other hand, the term that biases the weights towards the origin in NAC-CO, is removed when the constraints are inactive, \ie $c_j<0$.
  \item Therefore, the NAC-CO can track the desired trajectory without being biased, when the constraints are inactive.
}

@@

  \begin{itemize}
    \item<+-> NAC-CO (proposed) showed the \ctxt{airforceblue}{weight norms } are bounded \ctxt{awesome}{under pre-defined constraint } $\overline{\theta}=20$.
    \item<+-> NAC-L2 and NAC-eMod showed the bounded weight norms, but they \ctxt{awesome}{depended } on the parameters $\sigma$ and $\rho$, respectively.
    % \item<+-> As the parameters $\sigma$ and $\rho$ increase, the weight norms of NAC-L2 and NAC-eMod biased towards the origin, which may lead to suboptimal performance.
    \item<+-> In other words, NAC-CO tracked the desired trajectory with a \ctxt{airforceblue}{smaller weight } norm than NAC-L2 and NAC-eMod.
  \end{itemize}

@@

  \begin{itemize}
    \item NAC-CO (proposed) \ctxt{airforceblue}{outperformed } NAC-L2 and NAC-eMod in terms of \ctxt{awesome}{tracking performance}.
    \item As the weights are \ctxt{awesome}{biased }towards the origin proportionally to the parameters $\sigma$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward \ctxt{airforceblue}{suboptimal points}.
  \end{itemize}

@@

\note[enumerate]
{
  \item The tracking performance of the three methods are shown.
  \item The NAC-CO (proposed) outperformed the other two methods in terms of tracking performance.
  \item As the weights are biased towards the origin proportionally to the parameters $\sigma$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward suboptimal points.
}

@@

  \centering
  \includemedia[
      width=0.64\linewidth,
      height=0.36\linewidth,
      activate=onclick,
      addresource=assets/animation.mp4,
      flashvars={
        source=assets/animation.mp4
        &autoPlay=true
        &loop=true
      }
    ]{}{VPlayer.swf}

@@

  \textbf{Summary of Contributions}
  \begin{itemize}
    \item Proposed a constrained optimization-based neuro-adaptive control method.
    \item Adaptation laws are derived using \ctxt{airforceblue}{constrained optimization method}.
    \item The proposed method guarantees the \ctxt{awesome}{stability }of the system and the boundedness of the NN weights.
    \item Feasibility of the proposed method is validated through numerical simulations.
  \end{itemize}
